Probing internal structure of distant quasars using Microlensing

### 2014-04-15 paper1/ms.tex
first edits
all figures added

\author[I. Mohammed et al.] {Irshad Mohammed\thanks{irshad@physik.uzh.ch}$^1$,
Mihai Tomozeiu$^1$, Manuel Rabold$^1$,  Prasenjit Saha,$^1$ and Joachim Wambsgans$^2$\\
$^1${Institute for Theoretical Physics, University of Z$\ddot{u}$rich, 8057 Z$\ddot{u}$rich Switzerland}\\
$^2${University of Heidelberg, Germany}
}

@@

\begin{abstract}
We present a toy model to parametrize and constraint the innermost environment of a distant quasar using microlensing. 
\end{abstract}

@@

\citep{2006MNRAS.367.1209L}

@@

\def\apj{ApJ}
\def\apjl{ApJL}
\def\aj{AJ}
\def\mnras{MNRAS}
\def\aap{A\&A}

\bibliography{heap}

>>>>

\author[TBD] {TBD\thanks{}$^1$,
Mihai Tomozeiu$^1$, Manuel Rabold$^1$,  Prasenjit Saha,$^1$ and Joachim Wambsgans$^2$\\
$^1${Institute for Theoretical Physics, University of Z$\ddot{u}$rich, 8057 Z$\ddot{u}$rich Switzerland}\\
$^2${University of Heidelberg, Germany}
}

@@

\begin{abstract}

We present a toy model to parametrize and constraint the innermost environment of a distant quasar using microlensing. 
\end{abstract}

@@

@@

\def\apj{ApJ}
\def\apjl{ApJL}
\def\aj{AJ}
\def\mnras{MNRAS}
\def\aap{A\&A}
\def\nat{nature}
\def\araa{ARAA}
\def\pasa{PASA}
\bibliography{heap}
